Job Demands-Resources Model Components through the Lens of O*NET Classifications

### 2023-03-01 Submission.Rmd
edits made to RQ1 and RQ2.

In addition to the two hypotheses, two related research questions were proposed. To answer these research questions, authors first categorized items into the JD-R elements listed in the JD-R literature. For example, autonomy is frequently described as a resource. An O\*Net item in the autonomy category is, “How much decision making freedom, without supervision, does your job offer?”. This O\*Net item was therefore retained within the "autonomy" category. Means for resource, challenge, and hindrance groupings were then computed to explore whether literature-implicated resources and demands were evaluated as such. The left side of Figure 4 shows literature-derived demand categories (e.g., work pressure). Here, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as "high" gray and black bars and "low" white bars). In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be "hindrances" at work. However, in contrast, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings. The white bars representing resources are consistently higher. In sum, these results provide some support for RQ 1 and 2.

@@

Separate repeated-measures ANOVAs were conducted for each of these comparisons.

Repeated-measures ANOVAs were run for the group of literture-implicated demands first.  The effect for `Overwork` was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F`, partial eta squared $(\eta^2)$ was `r report1$ANOVA$pes`.
The effect for `Physical Environment` was $F_{(`r report2$ANOVA$DFn`, `r report2$ANOVA$DFd`)}$ = `r report2$ANOVA$F` ($\eta^2$ = `r report2$ANOVA$pes`).
The effect for `Time Pressure` was $F_{(`r report3$ANOVA$DFn`, `r report3$ANOVA$DFd`)}$ = `r report3$ANOVA$F` ($\eta^2$ = `r report3$ANOVA$pes`).
The effect for `Emotional Demands` was $F_{(`r report4$ANOVA$DFn`, `r report4$ANOVA$DFd`)}$ = `r report4$ANOVA$F` ($\eta^2$ = `r report4$ANOVA$pes`).
The effect for `Recipient Contact` was $F_{(`r report5$ANOVA$DFn`, `r report5$ANOVA$DFd`)}$ = `r report5$ANOVA$F` ($\eta^2$ = `r report5$ANOVA$pes`).
The effect for `Work Pressure` was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`).In all cases, statistical significance was less then .001, indicating in all cases, what the literature implicates is a demand was rated as a resource (all means are above the midpoint). See the patten of white resource bars on the lefthand side of Figure 4. This is contrary to the expectation that ratings would match our assumption of what a resource constitutes. Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.

Next, Repeated-measures ANOVAs were run for the group of literture-implicated resources (the right hand set of analyses presented in Figure 4). The effect for `Job Control` was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
The effect for `Participation` was $F_{(`r report8$ANOVA$DFn`, `r report8$ANOVA$DFd`)}$ = `r report8$ANOVA$F` ($\eta^2$ = `r report8$ANOVA$pes`).
The effect for `Autonomy` was $F_{(`r report9$ANOVA$DFn`, `r report9$ANOVA$DFd`)}$ = `r report9$ANOVA$F` ($\eta^2$ = `r report9$ANOVA$pes`).
The effect for `Team Cohesion` was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`).Similar to the demands analyses, statistical significance was less then .001 for all four category comparisons. Here, the pattern was as expected. Across categories, resources were rated the highest (see white bars representing resources in Figure 4).

>>>>

@@

In addition to the two hypotheses, two related research questions were proposed: 1) do literature-implicated resources materialize as perceived resources and 2) do literature-implicated demands materialize as perceived demands? To answer these questions, authors first categorized O\*Net items into the JD-R elements listed in the JD-R literature. For example, autonomy is frequently described as a resource in the JD-R literature. An O\*Net item in the autonomy category is, “How much decision making freedom, without supervision, does your job offer?”. This O\*Net item was therefore retained within the "autonomy" category. Mean ratings (of resource, challenge, and hindrances) were then computed to explore whether literature-implicated resources and demands were evaluated as such.

Repeated-measures ANOVAs were computed for the group of literature-implicated *resources* (see the right hand side of Figure 4). The effect for `Job Control` was $F_{(`r report7$ANOVA$DFn`, `r report7$ANOVA$DFd`)}$ = `r report7$ANOVA$F` ($\eta^2$ = `r report7$ANOVA$pes`).
The effect for `Participation` was $F_{(`r report8$ANOVA$DFn`, `r report8$ANOVA$DFd`)}$ = `r report8$ANOVA$F` ($\eta^2$ = `r report8$ANOVA$pes`).
The effect for `Autonomy` was $F_{(`r report9$ANOVA$DFn`, `r report9$ANOVA$DFd`)}$ = `r report9$ANOVA$F` ($\eta^2$ = `r report9$ANOVA$pes`).
The effect for `Team Cohesion` was $F_{(`r report10$ANOVA$DFn`, `r report10$ANOVA$DFd`)}$ = `r report10$ANOVA$F` ($\eta^2$ = `r report10$ANOVA$pes`).Statistical significance was less then .001 for all four category comparisons. Here, the pattern was as expected. Across categories, resources were rated the highest (see white bars representing resources in Figure 4). However, as can be seen, mean challenge (which is a demand) was rated quite similarly and above the midpoint of 3 across JD-R categories.

Next, repeated-measures ANOVAs were then run for the group of literature-implicated *demands*.  The effect for `Overwork` was $F_{(`r report1$ANOVA$DFn`, `r report1$ANOVA$DFd`)}$ = `r report1$ANOVA$F`, partial eta squared $(\eta^2)$ was `r report1$ANOVA$pes`. The effect for `Physical Environment` was $F_{(`r report2$ANOVA$DFn`, `r report2$ANOVA$DFd`)}$ = `r report2$ANOVA$F` ($\eta^2$ = `r report2$ANOVA$pes`). The effect for `Time Pressure` was $F_{(`r report3$ANOVA$DFn`, `r report3$ANOVA$DFd`)}$ = `r report3$ANOVA$F` ($\eta^2$ = `r report3$ANOVA$pes`). The effect for `Emotional Demands` was $F_{(`r report4$ANOVA$DFn`, `r report4$ANOVA$DFd`)}$ = `r report4$ANOVA$F` ($\eta^2$ = `r report4$ANOVA$pes`).
The effect for `Recipient Contact` was $F_{(`r report5$ANOVA$DFn`, `r report5$ANOVA$DFd`)}$ = `r report5$ANOVA$F` ($\eta^2$ = `r report5$ANOVA$pes`). The effect for `Work Pressure` was $F_{(`r report6$ANOVA$DFn`, `r report6$ANOVA$DFd`)}$ = `r report6$ANOVA$F` ($\eta^2$ = `r report6$ANOVA$pes`). In all cases, statistical significance was less then .001, indicating that what the literature implicates is a demand was actually rated as a resource (all resource means are above the midpoint). This is contrary to the expectation that ratings would match our assumption of what a resource constitutes. Looking at demands, there is a large difference between whether a characteristic is viewed as a challenge or hindrance.See the pattern of white resource bars on the lefthand side of Figure 4.

Figure 4 presents these comparisons visually. First exploring the right side of Figure 4, there is a clearer pattern of the highest level ratings being that of resources on the right side of Figure 4 showing literature-derived resources (e.g., job control) and the corresponding average category ratings. The white bars representing resources are consistently higher. As described above, the left side of Figure 4 shows literature-derived demand categories (e.g., work pressure). However, in contrast, we do not see a clear demarcation of resource and challenge, as would be expected if the job characteristics evidenced consistency (the literature-driven consistency would manifest as "high" gray and black bars and "low" white bars). In alignment with what we observed regarding variability in ratings of hindrance stressors in H1, there is much less consistency in how employees rated what should objectively be "hindrances" at work. In sum, these results provide some support for RQ 1 and 2.
